\vspace{-0.25em}\thetitle

### 2009-07-24 paper.tex
...

>>>>

\begin{abstract}
We have observed that when network traffic behaviors are embedded into vector spaces in certain ways, they tend to exhibit a great deal of low-rank linear structure.
This observation leads us to the hypothesis that flow behaviors follow a specific type of finite mixture model.
Aside from being of theoretical interest, this model has practical consequences:
it allows us, among other things, to make detailed predictions about the probabilities of various future flow behaviors after observing only a handful of a flow's initial packets.
This practical application serves a dual function.
It provides a highly useful tool of network management, especially in wireless networks where such predictions can be leveraged to better allocate scarce bandwidth resources.
But it also provides evidence that the hypothesized model not only explains the observed linear structure, but is actually an accurate model of real network traffic.
\end{abstract}
